---
title: "R Notebook"
output: html_notebook
---

```{r}

library(car)


df<-data.frame(mtcars)
y<-names(df)[1]
x<-names(df)[2:length(df)]
pvals<- vector()


x_final <- ""
j<-1
thresh<-2

#while(j<thresh){
  for(i in x){
    #print(i)
    model<- lm(paste(y,"~",i,"-1"),data=df)
    temp<-coef(summary(model))[,4]
    
    pvals[i]<-temp
    
    #print(pvals[i])
    
  }

    idx_min_p <- which.min(pvals)
    min_p_name <-names(pvals)[idx_min_p]
    min_p <- pvals[idx_min_p]
    print(pvals)
  if(min_p < .05 && length(x)>=1){
      #print(x)
      x<- x[-idx_min_p]
      #print(x)
      x_final <- paste(min_p_name,x_final,sep="+")
      #print(x_final)
      pvals <- vector()
      #next
  }
  #j<-thresh
#}
#print(x_final)
```

# T-test Forward Algorithm 

Start out with a set of $p$ number of response variables and create $p$ models, each with only $1$ of the variables in the set. From the $p$ number of models choose the one that yields the smallest p-value in T-test for signifigance. Then add the variable $p_1$ to the model $M$. The next iteration of models will contain $y ~ p_1$, add all $p$ variables to this model and choose the model that gives you the smallest p-value for the corresponding variable $p_i$ 
```{r}
###WORKING VERSION
library(car)

df<-data.frame(mtcars)
y<-names(df)[1]
x<-names(df)[4:length(df)]
pvals<- vector()
x_final <- ""
j<-1
thresh<-2

while(j<thresh){
if(x_final == ""){
for(i in x){
    formula <- paste(i,x_final,sep="+")
    formula <- paste(y,"~",formula,-1)
    #print(formula)
    model<- lm(formula = formula,data=df)
    print(coef(summary(model)))

    pvals[i] <- coef(summary(model))[,4]
    print(pvals[i])
    
}
    idx_min_p <- which.min(pvals)
    min_p_name <-names(pvals)[idx_min_p]
    min_p <- pvals[idx_min_p]
    print(pvals)
  if(min_p < .05 && length(x)>=1){
      #print(x)
      x<- x[-idx_min_p]
      #print(x)
      x_final <- paste(min_p_name,x_final,sep="+")
      #print(x_final)
      pvals <- vector()
      next
  }
}else{  
  for(i in x){
    formula <- paste(i,x_final,sep="+")
    formula <- paste(y,"~",formula,-1)
    
    model<- lm(formula = formula,data=df)
    print(coef(summary(model)))

    pvals[i] <- coef(summary(model))[,4][i]
    print(pvals[i])
    
  }
    idx_min_p <- which.min(pvals)
    min_p_name <-names(pvals)[idx_min_p]
    min_p <- pvals[idx_min_p]
    print(pvals)
    
  if(min_p < .05 && length(x)>=1){
      #print(x)
      x<- x[-idx_min_p]
      #print(x)
      x_final <- paste(min_p_name,x_final,sep="+")
      print(x_final)
      pvals <- vector()
      next
  }
} 
break
}
print(x_final)



```



```{r}
library(car)


df<-data.frame(mtcars)
y<-names(df)[1]
x<-names(df)[2:length(df)]
pvals<- vector()


for(i in x){
    formula <- paste(i,sep="+")
    formula <- paste(y,"~drat+carb+gear+",formula,-1)
    model<- lm(formula = formula,data=df)
    print(coef(summary(model))[,4])
}


```


```{r}
library(car)


df<-data.frame(mtcars)
y<-names(df)[1]
x<-names(df)[2:length(df)]
pvals<- vector()
model<-lm(mpg~-1,data=df)
print(summary(model))


```


```{r}

```

